Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-07 WSSSPE3/report/WSSSPE3_review.tex
add Stan Ahalt's talk

\item \textbf{Stan Ahalt, Bruce Berriman, Maxine Brown, Jeffrey Carver, Neil
Chue Hong, Allison Fish, Ray Idaszak, Greg Newman, Dhabaleswar Panda, Abani
Patra, Elbridge Gerry Puckett, Chris Roland, Douglas Thain, Selcuk Uluagac, and
Bo Zhang: \textit{Scientific Software Success: Developing Metrics While Developing
Community}}

>>>>

\item \textbf{Stan Ahalt, Bruce Berriman, Maxine Brown, Jeffrey Carver, Neil
Chue Hong, Allison Fish, Ray Idaszak, Greg Newman, Dhabaleswar Panda, Abani
Patra, Elbridge Gerry Puckett, Chris Roland, Douglas Thain, Selcuk Uluagac, and
Bo Zhang: \textit{Scientific Software Success: Developing Metrics While Developing
Community}}
The effort behind this talk started out as break-out team of an NSF SI2
workshop in 2015, and centeres around creating a framework for creation of
metrics for scientific software. This framework would improve both the metrics,
and the software it evaluates, and tries to build a community around this idea.
With especially the latter idea in mind, a software ``peer review group'' would
be created, respresenting stakeholders who will self-review software created by
their respective communities, and will concurrently develop metrics. The whole
project should be community-goverend, without a single institution overseeing
the activity or infrastructure, with the hope to evolving community-generated
and adopted standards. The generation of metrics would be tied to the actual
evaluation of software, creating incentive by improving the evaluated software
itself during this process. Infrastructure for the creationg of metrics and
evaluation would be provided by the framework code itself, but also provided
code reviews of the evaluated software, as well as socially through forums for
generation of software success metrics. With enough examples one of the open
questions is whether it is possible to fit the resulting metrics in a common
template. So far, this is still in a design phase, with a white paper at the
CSESSP workshop 2015 and this talk, but WSSPE workshop are seen as a forum for
the community to assemble and act, and are planned to be used also in the
future to build this community and framework.
